---
title: "R Notebook"
output: html_notebook
---


```{r}

mydata<-head(PlantGrowth)
sapply(PlantGrowth, mean, na.rm=TRUE)


head(PlantGrowth)

dim(PlantGrowth)

library(dplyr)
glimpse(PlantGrowth)

summary(PlantGrowth)

```

**Skim:** good addition to the summary function. Displaying 
- most the numerical attributes from summary, 
- it also displays missing values,
- more quantile information,
- and an inine histogram for each variable. 

```{r}
#install.packages("skimr")
library(skimr)
skim(PlantGrowth)

```


**create_report** 

```{r}
#install.packages("DataExplorer")
library(DataExplorer)

DataExplorer::create_report(PlantGrowth)
```

## Examine a Data Frame in R 

dim(): shows dimensions of data frames by row and column  
str(): shows the structure of the data frame  
head(): shows the first 6 rows of the data frame  
tail(): shows the first 6 rows of the data frame  
summary(): provides summary statistics on the columns of the data frames  
colnames(): shows the name of each column in the data frame  
View(): shows a spreadsheet-like display of the entire data frame

```{r}
dim(PlantGrowth)
str(PlantGrowth)
head(PlantGrowth)
tail(PlantGrowth)
summary(PlantGrowth)
colnames(PlantGrowth)
View(PlantGrowth)
```