---
title: "Building Shiny App"
output: html_notebook
---

There are several ways to create a Shiny app. The simplest is to create a new directory for your app, and put a single file called app.R in it. This app.R file will be used to tell Shiny both how your app should look, and how it should behave.
 

```{r}
library(shiny)
ui <- fluidPage(
  "Hello, world!"
)
server <- function(input, output, session) {
}
shinyApp(ui, server)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

## Adding UI Controls

Using built-in data frames in the dataset package.

```{r}
ui <- fluidPage(
  selectInput("dataset", label = "Dataset", choices = ls("package:datasets")),
  verbatimTextOutput("summary"),
  tableOutput("table")
)
```

- fluidPage() is a **layout function**, it sets up the basic visual structure of the page.  
- selectInput() is an **input control**, it allows users to interact with the app by providing a value.   
- verbatimTextOutput() and tableOutput() are **output controls**, they tell the app where to put rendered output. Specifically, verbatimTextOutput() displays code and tableOutput() displays tables. 

